### 2011-07-13 poster_gecco/poster.tex
Beautified!

    HyperNEAT is an indirect encoding for evolving artificial neural
    networks (ANNs) that is inspired by the way natural organisms
    develop~\cite{stanley2009hypercube}. It evolves Compositional
    Pattern Producing Networks
    (CPPNs)~\cite{stanley2007compositional}, each of which is a genome
    that encodes an ANN \pwfig{SpiderANN.jpg}{.7}{The ANN
      configuration used to generate gaits
      \cite{clune2011performance}.}\label{hyperneatLayout}
    phenotype~\cite{stanley2009hypercube}. Each CPPN is itself a
    directed graph, where the nodes in the graph are mathematical
    functions, such as sine or Gaussian. The nature of these functions
    can facilitate the evolution of properties such as symmetry
    (e.g.\ a Gaussian function) and repetition (e.g.\ a sine
    function)~\cite{stanley2009hypercube, stanley2007compositional}.

    For quadruped locomotion, HyperNEAT has previously produced gaits
    with front-back, left-right, and four-way
    symmetries~\cite{clune2009evolving, clune2011performance}.

@@

%Many effective HyperNEAT gaits were not preserved across generations
%because a single poor-performing trial could prevent their
%selection. The HyperNEAT learning curve would be smoother if the noise
%in the evaluations could be reduced or more than one evaluation per
%individual could be afforded.

\pfig{hnResults}{.8}{Average fitness ($\pm $ SE) of the highest
  performing individual at each generation.}

{\scriptsize
\begin{center}
\begin{tabular}{|r|c|c|c||c|}
\hline
                                         & Avg & SD \\
\hline                                    
\hline                                    
Previous hand-coded gait                 & 5.16   &   --     \\
\hline
Random search                            & 9.40   &   6.83   \\
\hline
Uniform Hill Climbing             & 7.83   &   4.56   \\
\hline
Gaussian Hill Climbing            & 10.03  &   6.00   \\
\hline
Policy Gradient Descent                  & 6.32   &   7.39   \\
\hline
Nelder-Mead simplex                      & 12.32  &   3.35   \\
\hline
Linear Regression                        & 14.01  &  12.88   \\
\hline
Evolved Neural Network              &        &          \\
(HyperNEAT)                              & 29.26  &   6.37   \\
\hline
\end{tabular}
\capt{Average and SD of the best gaits found
  during each of three runs, in body
  lengths/minute.}  \tablabel{results}
\end{center}
}

@@

    \scriptsize
    \bibliography{references.bib}
    \bibliographystyle{is-plain}
  }%
\end{poster}%
%
\end{document}

>>>>

    HyperNEAT is an indirect encoding for evolving artificial neural
    networks (ANNs) that is inspired by the way natural organisms
    develop~\cite{stanley2009hypercube}. It evolves Compositional
    Pattern Producing Networks
    (CPPNs)~\cite{stanley2007compositional}, each of which is a genome
    that encodes an ANN 
    phenotype~\cite{stanley2009hypercube}. Each CPPN is itself a
    directed graph, where the nodes in the graph are mathematical
    functions, such as sine or Gaussian. The nature of these functions
    can facilitate the evolution of properties such as symmetry
    (e.g.\ a Gaussian function) and repetition (e.g.\ a sine
    function)~\cite{stanley2009hypercube, stanley2007compositional}.

    \pfig{SpiderANN.jpg}{.8}{ANN
      configuration to generate gaits
      \cite{clune2011performance}.}\label{hyperneatLayout}
    For quadruped locomotion, HyperNEAT has previously produced gaits
    with front-back, left-right, and four-way
    symmetries~\cite{clune2009evolving, clune2011performance}.

@@

Many effective HyperNEAT gaits were not preserved across generations
because a single poor-performing trial could prevent their
selection. The HyperNEAT learning curve would be smoother if the noise
in the evaluations could be reduced or more than one evaluation per
individual could be afforded.

\pfig{hnResults}{1}{Average fitness ($\pm $ SE) of the highest
  performing individual at each generation.}

\textbf{Overall}
\vspace{.5em}

{\scriptsize
\begin{center}
\begin{tabular}{|r|c|c|c||c|}
\hline
                                         & Avg & SD \\
\hline                                    
\hline                                    
Previous hand-coded gait                 & 5.16   &   --     \\
\hline
Random search                            & 9.40   &   6.83   \\
\hline
Uniform Hill Climbing             & 7.83   &   4.56   \\
\hline
Gaussian Hill Climbing            & 10.03  &   6.00   \\
\hline
Policy Gradient Descent                  & 6.32   &   7.39   \\
\hline
Nelder-Mead simplex                      & 12.32  &   3.35   \\
\hline
Linear Regression                        & 14.01  &  12.88   \\
\hline
Evolved Neural Network              &        &          \\
(HyperNEAT)                              & 29.26  &   6.37   \\
\hline
\end{tabular}
\vspace{.5em}\\
\capt{Average and SD of the best gaits found
  during each of three runs, in body
  lengths/minute.}  \tablabel{results}
\end{center}
}

@@

    \scriptsize

    \bibliography{references.bib}
    %\bibliographystyle{is-plain}
    \bibliographystyle{plain}
  }%
\end{poster}%
%
\end{document}
